Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-07 formally.tex
updated version of movement erasure that resolves the question about pin, and is a much more uniform description. close #3.
typo

Types and expressions that contain no holes are \emph{complete types} and
\emph{complete expressions}, respectively. Formally, we can derive
$\hcomplete{\htau}$ when $\htau$ is complete, and $\hcomplete{\hexp}$ when
$\hexp$ is complete (see supplement.) We are not concerned here with
defining a dynamic semantics for Hazelnut, but the dynamics for complete
H-expressions would be entirely standard (in Sec. \ref{sec:rw} we discuss
the multi-dimensional design space around the question of evaluating
incomplete H-expressions.) For completeness, a mapping from the
bidirectional type system to a declarative one, and a of type safety for
complete terms in that system, is included in the mechanization.

@@

  \item If
    $\performSyn{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}{\htau}$
    then $\removeSel{\zexp}=\removeSel{\zexp'}$.

  \item If $\performAna{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}$
    then $\removeSel{\zexp}=\removeSel{\zexp'}$.

>>>>

Types and expressions that contain no holes are \emph{complete types} and
\emph{complete expressions}, respectively. Formally, we can derive
$\hcomplete{\htau}$ when $\htau$ is complete, and $\hcomplete{\hexp}$ when
$\hexp$ is complete (see supplement.) We are not concerned here with
defining a dynamic semantics for Hazelnut, but the dynamics for complete
H-expressions would be entirely standard (in Sec. \ref{sec:rw} we discuss
the multi-dimensional design space around the question of evaluating
incomplete H-expressions.) For completeness, a mapping from the
bidirectional type system to a declarative one, and a proof of type safety
for complete terms in that system, is included in the mechanization.

@@

  \item If $\hsyn{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\performSyn{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}{\htau'}$
    then $\removeSel{\zexp}=\removeSel{\zexp'}$ and $\htau=\htau'$.

  \item If $\hana{\hGamma}{\removeSel{\zexp}}{\htau}$ and
    $\performAna{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}$ then
    $\removeSel{\zexp}=\removeSel{\zexp'}$.
